---
title: "README"
author: "Dian"
date: "04 September 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

################################
# Assignment-17158567-Dian Kotze
################################

#loading the required packages
loading rmsfuns
```{r}
library(rmsfuns)
```
load_pkg(packagelist = packagestoload)
```{r}
packagestoload <- c("xts", "tidyverse", "tbl2xts", "PerformanceAnalytics", 
                    "lubridate", "glue")
```
load_pkg("ggplot2")


#Building path for respective folders
```{r}
Practical.loc.root <- file.path("C:/Users/Dian Kotze/Documents/FinMetrics/assignment/index_return_comparison")
Practical.loc.subdirs <- c("data", "code", "bin")
PracLoc <- build_path(glue::glue("{Practical.loc.root}/{Practical.loc.subdirs}"))
```

Loading the data
```{r}
library(tidyverse)
Daily_TRI <-
  read_rds("C:/Users/Dian Kotze/Documents/FinMetrics/assignment/index_return_comparison/Fin_Data_SA_US_NKY.rds")

```
omitting the NA's
```{r}
Daily_TRI_NA_omit <- Daily_TRI %>% 
  na.omit()
```

1) Calculating the cap-weighted monthly index returns for every sector for each country.

```{r}
Cap_Weighted_monthly_index_ret <- Daily_TRI_NA_omit %>% 
  mutate(Year_Month = format(date,"%Y_%B")) %>%
  group_by(Year_Month, Ticker) %>% 
  filter(date == last(date)) %>%
  ungroup() %>% 
  
#Calculate monthly returns from TRI
  group_by(Ticker) %>% 
  mutate(Monthly_Returns = TRI/lag(TRI)-1) %>%
  mutate(Monthly_Returns = coalesce(Monthly_Returns, 0)) %>%
  ungroup() %>%
  
#adding up the market cap per sector
  group_by(Universe, BICS_LEVEL_1_SECTOR_NAME, date) %>% 
  mutate(sec_cap = sum(Market.Cap)) %>% 
  
#divide each country by market sector to get weight of index
  mutate(w_index = Market.Cap/sec_cap) %>% 
  
#multiply each observation return by weight
  mutate(w_portfolio_ret = sum(Monthly_Returns*w_index)) %>% 
  summarise(w_monthly_returns = mean(w_portfolio_ret)) %>%
  ungroup()
```

2) Calaculate the sharpe ratio for the equally weighted by country, cap-weighted index returns since 2017.

```{r}
Cap_w_monthly_index_sharp_ret <- 
  Cap_Weighted_monthly_index_ret %>% 
  group_by(Universe, BICS_LEVEL_1_SECTOR_NAME) %>% 
  # sharpe ratio's
  summarise(Sharpe = mean(w_monthly_returns, na.rm = TRUE) / sd(w_monthly_returns, na.rm = TRUE)) %>% 
  ungroup() 
```

3) Plotting Cumulative returns for financials of the 3 countries
```{r}
Financial_sectors <- Cap_Weighted_monthly_index_ret %>% 
  filter(BICS_LEVEL_1_SECTOR_NAME %in% c( "Financials")) %>% 
  group_by(Universe) %>%
  mutate(Cum_Return = cumprod( 1 + w_monthly_returns)) 

# Plotting financial sector
ggplot(Financial_sectors) + 
  geom_line(aes(date, Cum_Return, color = Universe))
```

4) Calculating the JALSH index returns, by filtering the top 95% of Market Cap
```{r}
JALSH_95_top_ret <- Daily_TRI_NA_omit %>%
  group_by(Ticker) %>%
  filter(Universe %in% c("JALSHAll")) %>% 
  mutate(d_returns= TRI/ lag(TRI)-1) %>%  # Override Return column NAs....
  mutate(d_returns = coalesce(d_returns, 0)) %>% 
  ungroup() %>% 
#calculate weighted returns and filter top 95% of market cap
  group_by(date) %>% 
  mutate(jalsh_cap = sum(Market.Cap)) %>%  
  mutate(jalsh_w = Market.Cap/jalsh_cap) %>% 
  mutate(Cum_w = cumsum(jalsh_w)) %>% 
  filter(Cum_w >= 0.05) %>% 
  mutate(w_portfolio_return = sum(d_returns*jalsh_w)) %>%
  summarise(lalsh_return = mean(w_portfolio_return)) %>% 
  ungroup()
```

5) Rolling 60 day standard deviation for the Materials sectors of each country

```{r eval=FALSE}
Rolling_60_day_materials <- Daily_TRI_NA_omit %>%
  filter(BICS_LEVEL_1_SECTOR_NAME %in% "materials") %>% 
  group_by(Ticker) %>% 
  mutate(Returns = TRI/lag(TRI)-1) %>%
  mutate(Returns = coalesce(Returns, 0)) %>%
  ungroup() %>% 
  group_by(Universe, date) %>%
  mutate(sec_cap = sum(Market.Cap)) %>% 
  mutate(w_index = Market.Cap/sec_cap) %>% 
  mutate(w_return= sum(Returns*w_index)) %>% 
  summarise(w_materials_returns = mean(w_return)) %>%
  ungroup() %>% 
  tbl_xts(., cols_to_xts = "w_materials_returns", spread_by = "Universe")

chart.RollingPerformance(R = Rolling_60_day_materials, FUN = "sd", 
                         width = 4, main = "Rolling 60 Day Standard Deviation", 
                         legend.loc = "bottomleft")
```


